---
title: "Prediction Assignment"
author: "Trevor"
date: "4 October 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive summary
This assignment is to predict the manner in which a group of excercise enthusiasts did their exercise. 

##Pre-processing
Read Training and Test Data
```{r warning=FALSE}
library(caret)
library(randomForest)
set.seed(158)
train_data <- read.csv("pml-training.csv")
test_data <- read.csv("pml-testing.csv")
```
Clean the data by removing near zeros and N/As
```{r}
#Remove near zero
NZ <- nearZeroVar(train_data)
train_data <- train_data[,-NZ]

#Remove greater than 90% N/As
NAs <- sapply(train_data, function(x) mean(is.na(x))) > 0.9
train_data <- train_data[,NAs==F]
```
##Remove variables that won't impact prediction (i.e. X, username, timestamp)
```{r}
train_data <- train_data[,-(1:5)]
```

##Use Machine Learning: Random Forest and 3-fold cross validation
```{r}
fit <- train(classe ~., method="rf",data=train_data,trControl=trainControl(method="cv",number=3))

fit$finalModel
```

##Make predictions
```{r}
prediction <- predict(fit,newdata=test_data)
```

Get the the prediction as characters
```{r}
prediction <- as.character(prediction)
prediction
```